 \vspace{0.3ex}
\noindent\textbf{Activity 4.7}

\vspace{0.2ex}


For each problem below, use the Fundamental Counting Principle to determine the number of possible outcomes.
%\begin{multicols}{2}
\setlist{nolistsep}
\begin{enumerate}[noitemsep, label = \color{blue}\arabic*. ]
%    \item \textbf{Choosing a Hat and Shoes}: You have 4 hats (black, white, red, blue) and 2 pairs of shoes (brown, black). How many different combinations can you create?

 %   \item \textbf{Flipping Three Coins}: You flip three coins. How many possible outcomes are there?

  %  \item \textbf{Rolling a Die and Picking a Card}: You roll a six-sided die and pick a card from a deck of 4 cards labeled A, B, C, D. How many possible outcomes are there?

   % \item \textbf{Choosing a Snack, Drink, and Dessert}: You can choose 1 snack from 4 options, 1 drink from 3 options, and 1 dessert from 2 options. How many different combinations of snacks, drinks, and desserts can you create?

    %\item \textbf{Rolling Three Dice}: You roll three six-sided dice. How many different outcomes are there?

    \item \textbf{Choosing Two Movies}: You are choosing 2 movies from a selection of 6 movies. How many different pairs of movies can you choose?

    \item \textbf{Making a Pizza}: You are making a pizza. You can choose 2 types of crust (thin, thick), 3 types of sauce (tomato, white, pesto), and 4 toppings (pepperoni, mushrooms, onions, sausage). How many different pizzas can you create?

    \item \textbf{Creating a PIN Code}: A PIN must consist of 4 digits. How many different PIN codes are possible if you can choose from 10 digits?

    \item \textbf{Spinning Three Spinners}: One spinner has 3 sections labeled X, Y, Z. Another spinner has 2 sections labeled 1, 2. A third spinner has 4 sections labeled A, B, C, D. How many different outcomes are possible?

    \item \textbf{Choosing a Drink and Snack}: You are picking a drink from 5 options (milk, coffee, tea, juice, soda) and a snack from 2 options (cookies, fruit). How many different combinations of drinks and snacks can you choose?
\end{enumerate}


