\begin{center}
\textbf{Lesson 1.10.2: Solving Real-Life Problems Using Quadratic Functions}
\end{center}

\vspace*{1ex}

\textbf{Steps for Solving Real-Life Problems Using Quadratic Functions}
\begin{enumerate}
    \item \textbf{Understand the Problem:}
    \begin{itemize}
        \item Read the problem carefully and identify what is being asked.
        \item Determine the relevant quantities and variables involved in the problem.
    \end{itemize}
    
    \item \textbf{Model the Situation:}
    \begin{itemize}
        \item Choose an appropriate quadratic function that represents the relationship between the variables.
        \item Decide whether the problem can be modeled using standard form, vertex form, or factored form of a quadratic function.
    \end{itemize}
    
    \item \textbf{Formulate the Equation:}
    \begin{itemize}
        \item Write down the equation that represents the problem using the chosen quadratic function.
        \item Ensure that the equation is in a form that can be easily solved, such as standard form or vertex form.
    \end{itemize}
    
    \item \textbf{Solve the Equation:}
    \begin{itemize}
        \item Use appropriate methods to solve the quadratic equation, such as factoring, completing the square, or using the quadratic formula.
        \item Determine the solutions and interpret them in the context of the problem.
    \end{itemize}
    
    \item \textbf{Check the Solution:}
    \begin{itemize}
        \item Verify that the solutions make sense in the context of the problem.
        \item Check for extraneous solutions or unrealistic solutions.
    \end{itemize}
\end{enumerate}

