%\vspace{1ex}
\vspace{0.3ex}
\noindent\textbf{Activity 3.04}

%\vspace{0.75ex}
\vspace{0.2ex}

Use the information provided in each graph to answer the questions below.

\begin{enumerate}[label=\color{blue}\arabic*.]
    \item \textbf{Bar Graph Interpretation} \\
    A bar graph shows the number of books read by students in one month:

    \begin{center}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Student} & \textbf{Books Read} \\
        \hline
        Anna & 5 \\
        Ben & 8 \\
        Carol & 7 \\
        Daniel & 4 \\
        \hline
    \end{tabular}
    \end{center}

    \begin{enumerate}[label=(\alph*)]
        \item Which student read the most books?
        \item How many books did Anna and Daniel read in total?
        \item What is the difference in books read between Ben and Carol?
    \end{enumerate}

    \item \textbf{Pie Chart Interpretation} \\
    A pie chart shows how a group of students spend their free time:
    
    \begin{itemize}
        \item Reading: 40\%
        \item Sports: 30\%
        \item Watching TV: 20\%
        \item Other Activities: 10\%
    \end{itemize}
    
    \begin{enumerate}[label=(\alph*)]
        \item Which activity takes up the most time?
        \item What percentage of time is spent on activities other than sports?
        \item If there are 100 students, how many spend time on "Other Activities"?
    \end{enumerate}

    \item \textbf{Line Graph Interpretation} \\
    A line graph shows the temperature in degrees Celsius over one week in a town:

    \begin{center}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Day} & \textbf{Temperature (°C)} \\
        \hline
        Monday & 18 \\
        Tuesday & 20 \\
        Wednesday & 22 \\
        Thursday & 21 \\
        Friday & 19 \\
        Saturday & 24 \\
        Sunday & 23 \\
        \hline
    \end{tabular}
    \end{center}

    \begin{enumerate}[label=(\alph*)]
        \item Which day had the highest temperature?
        \item What was the temperature difference between Tuesday and Friday?
        \item Was there an overall increase or decrease in temperature over the week?
    \end{enumerate}
    
    \item \textbf{Histogram Interpretation} \\
    A histogram shows the ages of participants in a community event:

    \begin{center}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Age Range} & \textbf{Frequency (Number of People)} \\
        \hline
        10-15 & 5 \\
        16-20 & 12 \\
        21-25 & 8 \\
        26-30 & 10 \\
        \hline
    \end{tabular}
    \end{center}

    \begin{enumerate}[label=(\alph*)]
        \item Which age range has the most participants?
        \item How many participants are younger than 20?
        \item What is the total number of participants?
    \end{enumerate}
\end{enumerate}

