%\vspace{1ex}
\vspace{0.3ex}
\noindent\textbf{Practice Exercises 3.04}

%\vspace{0.75ex}
\vspace{0.2ex}

Use the information provided in each graph to answer the questions below.

\begin{enumerate}[label=\color{blue}\arabic*.]
    \item \textbf{Bar Graph Interpretation} \\
    A bar graph shows the number of pets owned by students in one class:

    \begin{center}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Student} & \textbf{Pets Owned} \\
        \hline
        Emily & 3 \\
        Frank & 6 \\
        Grace & 5 \\
        Henry & 2 \\
        \hline
    \end{tabular}
    \end{center}

%<<external-code, cache=FALSE,echo=F>>=
%read_chunk('Rcode.R')
%@

%<<external-code,echo=F>>=
%@

    \begin{enumerate}[label=(\alph*)]
        \item Which student owns the most pets?
        \item How many pets do Emily and Henry own in total?
        \item What is the difference in pets owned between Frank and Grace?
    \end{enumerate}

    \item \textbf{Pie Chart Interpretation} \\
    A pie chart shows how students prefer to travel to school:
    
    \begin{itemize}
        \item Walking: 25\%
        \item Biking: 35\%
        \item Bus: 30\%
        \item Carpool: 10\%
    \end{itemize}
    
    \begin{enumerate}[label=(\alph*)]
        \item Which mode of travel is the most preferred?
        \item What percentage of students prefer to travel by bus or carpool?
        \item If there are 80 students surveyed, how many prefer to walk to school?
    \end{enumerate}

    \item \textbf{Line Graph Interpretation} \\
    A line graph shows the sales of a lemonade stand over a week:

    \begin{center}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Day} & \textbf{Sales (\$)} \\
        \hline
        Monday & 25 \\
        Tuesday & 30 \\
        Wednesday & 28 \\
        Thursday & 35 \\
        Friday & 40 \\
        Saturday & 50 \\
        Sunday & 45 \\
        \hline
    \end{tabular}
    \end{center}

    \begin{enumerate}[label=(\alph*)]
        \item Which day had the highest sales?
        \item What was the sales difference between Tuesday and Thursday?
        \item Was there an overall increase or decrease in sales over the week?
    \end{enumerate}
    
    \item \textbf{Histogram Interpretation} \\
    A histogram shows the hours spent on homework by students in a week:

    \begin{center}
    \begin{tabular}{|c|c|}
        \hline
        \textbf{Hours Spent} & \textbf{Frequency (Number of Students)} \\
        \hline
        0-2 & 7 \\
        3-5 & 10 \\
        6-8 & 8 \\
        9-11 & 5 \\
        \hline
    \end{tabular}
    \end{center}

    \begin{enumerate}[label=(\alph*)]
        \item Which range of hours has the most students?
        \item How many students spend less than 6 hours on homework?
        \item What is the total number of students surveyed?
    \end{enumerate}
\end{enumerate}
