 \vspace{0.3ex}
\noindent\textbf{Activity 3.5}

\vspace{0.2ex}

Solve the following real-world problems using linear inequalities.
%\begin{multicols}{2}
\setlist{nolistsep}
\begin{enumerate}[noitemsep, label = \color{blue}\arabic*. ]
%    \item You need to buy notebooks for a class project. Each notebook costs \$1.25, and you have \$10. Write and solve an inequality to determine how many notebooks you can buy.
 %   \item The maximum weight limit of a boat is 800 kg. If each passenger weighs an average of 80 kg, write and solve an inequality to determine how many passengers can safely board the boat.
  %  \item A streaming service charges \$12 per month, and you have a budget of \$50. Write and solve an inequality to determine how many months you can afford the service.
   % \item You want to buy a book that costs \$25. If you already have \$5 and save \$3 per week, write and solve an inequality to find how many weeks it will take you to save enough money.
   % \item A carpenter has 100 meters of wood to build a fence. The length of the fence is 30 meters. Write and solve an inequality to find the possible heights of the fence.
    \item You are renting a kayak for the day. The rental company charges \$10 per hour, and you have a maximum of \$80 to spend. Write and solve an inequality to determine how many hours you can rent the kayak.
    \item To qualify for a competition, you need at least 75\% of the total score. The test has 40 questions, and you’ve answered 20 correctly. Write and solve an inequality to find how many more questions you need to answer correctly to qualify.
    \item A water tank can hold up to 5,000 liters of water. You’ve already filled it with 3,000 liters, and water flows at a rate of 200 liters per minute. Write and solve an inequality to determine how many more minutes you can keep filling the tank.
    \item You are purchasing movie tickets for a group of friends. Each ticket costs \$15, and you have a budget of \$120. Write and solve an inequality to determine how many tickets you can buy.
    \item A moving company charges \$50 per day plus \$0.25 per mile driven. If you have a budget of \$200, write and solve an inequality to determine how many miles you can drive.
\end{enumerate}


