%\vspace{1ex}
\vspace{0.3ex}
\noindent\textbf{Activity 3.18}

%\vspace{0.75ex}
\vspace{0.2ex}

Solve the following problems. 

\begin{enumerate}[label=\color{blue}\arabic*.]
    \item In a class of 45 students, 20 like Math, 30 like Science, and 15 like both. How many students like either Math or Science?
    \item In a group of 60 students, 25 like Soccer, 40 like Basketball, and 20 like both. How many students like either Soccer or Basketball?
    \item In a survey of 110 students, 70 like Reading, 80 like Traveling, and 60 like both. How many like either Reading or Traveling?
    \item A company surveyed 150 employees. 90 like coffee, 110 like tea, and 80 like both. How many employees like either coffee or tea?
    \item In a group of 70 students, 50 like Soccer, 60 like Basketball, and 40 like both. How many students like either Soccer or Basketball?
    \item In a survey of 180 people, 120 like running, 140 like cycling, and 100 like both. How many people like either running or cycling?
    \item In a group of 220 students, 130 like movies, 160 like music, and 120 like both. How many students like either movies or music?
    \item In a survey of 140 students, 80 like chocolate, 90 like vanilla, and 70 like both. How many students like either chocolate or vanilla?
    \item In a group of 270 people, 180 like swimming, 200 like cycling, and 170 like both. How many people like either swimming or cycling?
    \item In a survey of 200 people, 150 like basketball, 160 like football, and 130 like both. How many people like either basketball or football?
\end{enumerate}
