%\vspace{1ex}
\vspace{0.3ex}
\noindent\textbf{Activity 3.23}

%\vspace{0.75ex}
\vspace{0.2ex}

Calculate \( P(A \cup B) \) given the information from the Venn diagram.

\begin{enumerate}[label=\color{blue}\arabic*.]
    \item In a group of 120 people, 50 like basketball (set \( A \)), 40 like soccer (set \( B \)), and 20 like both basketball and soccer.  
    \item A deck of 52 cards is shuffled. Let event \( A \) be drawing a red card (26 red cards), event \( B \) be drawing a king (4 kings), and event \( A \cap B \) be drawing the king of hearts (1 card).  
    \item In a class of 60 students, 35 are in the school band (set \( A \)), 30 are on the sports team (set \( B \)), and 15 students are in both the band and the sports team.  
    \item A survey of 300 people shows that 180 like reading (set \( A \)), 120 like traveling (set \( B \)), and 90 like both reading and traveling.  
    \item In a bag of marbles, 80 marbles are red (set \( A \)), 50 marbles are blue (set \( B \)), and 30 marbles are both red and blue.  
    \item A study shows that 200 people like tea (set \( A \)), 150 like coffee (set \( B \)), and 80 like both tea and coffee.  
    \item In a survey, 700 people are asked about their favorite hobbies. 350 people like gardening (set \( A \)), 280 people like painting (set \( B \)), and 140 people like both.  
    \item In a school, 200 students are enrolled in math (set \( A \)), 180 are enrolled in science (set \( B \)), and 90 students are enrolled in both subjects.  
    \item A spinner has 12 sections, 4 of which are red (set \( A \)), 5 are blue (set \( B \)), and 3 are both red and blue.  
    \item In a class of 40 students, 20 students like apples (set \( A \)), 15 students like bananas (set \( B \)), and 10 students like both apples and bananas.  
\end{enumerate}
