 \vspace{0.3ex}
\noindent\textbf{Practice Exercises 4.11}

\vspace{0.2ex}


A. Determine whether experimental or theoretical probability is used in each of the following cases.  
\begin{enumerate} 
%1
\item Cyril and Alyssa played a Pinoy game 20 times. Cyril won 12 times. The probability that Alyssa will lose the next game is 0.4.
%2
\item The probability getting a sum of 8 in throwing a pair of dice is $\dfrac{5}{36}$. 
%3
\item Bernadette tossed a coin 150 times and got 81 heads and 69 tails. The probability of getting a head is 0.54.
%4
\item Anita surveyed 200 families in the barangay and recorded the number of children in each family. The survey results showed that 110 families had 2 children and 90 families had more than 2 children. The probability that the number of families with 2 children is 0.55.
%5
\item The probability of getting at least 3 heads in tossing a coin thrice is $\dfrac{1}{8}$. 
%6
\item The probability of drawing a red ball from a jar that contains 12 red balls, 15 blue balls and 7 white balls is 0.353.
%7
\item The probability of choosing a senior from 25 seniors and 25 juniors is $\dfrac{1}{2} $. 
\item If the probability that a 50-year old man will still live at 70 is 37\%, then the probability that the man will die before the age of 70 years is 63\%.
\end{enumerate}

B. Solve each problem completely.

\begin{enumerate} 
%1
\item A coin was tossed 100 times. It fell on tails 43 times. What is the experimental probability that it falls: 
\begin{enumerate}
\begin{multicols}{2}
%1
\item  Heads
%2
\item  Tails
\end{multicols}  
\end{enumerate}   
%2
\item A pair of coin is tossed 400 times and the results are:

\begin{center}
%\scalebox{0.9}{ 
\noindent\begin{minipage}{0.45\textwidth}
\begin{tabularx}{\textwidth}{|Y|Y|Y|Y|}
\hline
\textbf{Result} & Two heads & Two tails & A head and a tail\\
\hline
\textbf{Frequency} & 104 & 199 & 97\\
\hline
\end{tabularx} 
\end{minipage}
%}
\end{center} 

What is the experimental probability of getting: 
\begin{enumerate}
\begin{multicols}{3}
%a
\item  Two heads 
%b
\item  A head and a tail
%c
\item  Two tails
\end{multicols}  
\end{enumerate} 

%3
\item A 52-card pack is well shuffled and then one card is drawn from the top of the pack. Determine that it is: 
\begin{enumerate}
\begin{multicols}{3}
%a
\item  A jack
%b
\item  A diamond
%c
\item  A red card
\end{multicols}
\end{enumerate} 

%1
\item Three coins are tossed. What is the probability of getting:
\begin{multicols}{3}
\begin{enumerate}
%a
\item three heads
%b
\item at least two tails
%c
\item at most two tails

\end{enumerate} 
\end{multicols} 
%2

\end{enumerate}  


